Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes
vspace

The advantages of automatic memory management is important for successful execution of any application. This thesis focuses on concurrent programs and automatic memory management requirement in concurrent programs.

Concurrent programs are termed used to describe multiple programs running simultaneously to perform some computation. There are two different environments where concurrent programs are used : Shared memory and distributed memory systems. Shared memory systems contain multiple processors / multi-core processors sharing a common memory and execute the computation through threads / processes. Thread communicate using shared memory and may use atomic instructions or traditional lock to execute some critical sections of the program. 
In shared memory environment, concurrent programmers use smart pointers to manually manage memory. Smart pointers are manual reference counting technique implemented by application programming interface. Distributed memory systems contain multiple processors with dedicated memory and processors are separated by some physical distance and connected via the network. In Distributed memory systems, processes on each processor and processes communicate by sending messages across the network to perform the computation. Both of the environment contain programs that run concurrently and requires some form of communication to perform desired computation. The distinction between both of the environments are communication technique used and memory. Both of the environments uses automatic memory management feature to help developers build applications with above-mentioned benefits.

>>>>

\vspace{0.2in}
The advantages of automatic memory management is important for successful execution of any application. This thesis focuses on concurrent programs and automatic memory management requirement in concurrent programs.

Concurrent program is a term used to describe multiple thread / process running simultaneously to perform some computation. There are two different environments where concurrent programs are used: Shared memory and distributed memory systems. Shared memory systems contain multiple processors / multi-core processors sharing a common memory and execute the computation through threads / processes. Thread communicate using shared memory and may use atomic instructions or traditional lock to execute some critical sections of the program. 
In shared memory environment, concurrent programmers use smart pointers to manually manage memory. Smart pointers are manual reference counting technique implemented by application programming interface. Distributed memory systems contain multiple processors with dedicated memory and processors are separated by some physical distance and connected via the network. In Distributed memory systems, processes on each processor and processes communicate by sending messages across the network to perform the computation. Both of the environment contain programs that run concurrently and requires some form of communication to perform desired computation. The distinction between both of the environments are communication technique used and memory. Both of the environments uses automatic memory management feature to help developers build applications with above-mentioned benefits.
